Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-21 stp/paper_aaai/main.tex
Merged with the version Natalia sent via email, and shortened the paper a lot

\usepackage{tikz}
\tikzset{every picture/.style={font issue=\small},
         font issue/.style={execute at begin picture={#1\selectfont}}
        }
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[ellipse,align=center,fill=green!25]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=0.3,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

\newcommand{\minizinc}{\textsc{MiniZinc}}
\newcommand{\chuffed}{\textsc{Chuffed}}
\newcommand{\relonto}{\textsc{Rel2Onto}}

@@

Firstly, we build an \emph{integration graph} which includes the 
attributes from the new source as well as ontology classes and properties. 
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use Constraint Programming (CP) to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting Steiner Tree is a valid and coherent semantic model for the new source.

@@

Section \ref{SEC:pw} presents the previous work done to achieve this task. 
Section \ref{SEC:problem} formally states the problem. 
In Section \ref{SEC:ML} we present how we convert the information given into a 
useful data representation. 
Section \ref{SEC:STP} shows how we model the problem as a STP, 
whereas Section \ref{SEC:CP} discusses how we implement the model in CP. 
Section \ref{SEC:Res} shows our results.

@@

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
 We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. 
The edges in the semantic model correspond to object properties in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of the same ontology class or object property.

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number of whitespaces and other special characters, statistics of values in the column (e.g, mean/ max/ min string length and numeric statistics) and many more.
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

Note that we keep all the matches, regardless of the confidence fo the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics to then simplify the task of 
finding the semantic model. \ddg{CHECK}

@@

The algorithm for the construction of the alignment graph $\mathcal{G_O}$ follows the ideas of~\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
%\begin{enumerate}
$(i)$ %\item 
Adding the known semantic models
$(ii)$ %\item 
Adding the semantic types learned for the target source \ddg{If we keep 
all matches, isn't this just adding all the semantic types?}
%\item 
$(iii)$ Expanding the graph using the domain ontology $\mathcal{O}$.
%\end{enumerate}

Note how the alignment graph contains data nodes that correspond to at least 
some of the semantic types. 
For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
nodes $City$ and $State$. 
We say these nodes are \emph{induced} into the 
alignment graph by the semantic types.
We denote them as $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ in 
such a way that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
As we will see in the next section, this makes edges present in semantic models more attractive. \ddg{How exactly are 
they weighted?}

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange ones correspond to the ones added to connect Classes of the ontology that never appeared in the semantic models) and can be assigned the 
maximum weight $w_max$ \ddg{where does this weight come from?}

@@

	\node[class,fill=orange!30!white] (PL) at (3,\ysh/2)  {\small Place};

@@

\end{tikzpicture}
\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
{};}' and `\tikz{ \node[class,fill=orange!30!white] () at (0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\end{figure}

@@

We associate a weighting function  $w_\mathcal{I} : E \mapsto \mathbb{R}^+$ to 
the integration graph. For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
w_\mathcal{O}(e)$. For an edge $e 
\in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
$l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
ln(\psi(a_i,l_i))$. \ddg{CHECK!}

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a reprocess that requires extra time and effort as this is typically done manually in the real world.

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The rest of the attributes can then be matched normally 
and build  a semantic model as usual. 
Then, to maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the selected Class nodes will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} won't be selected in the 
Steiner tree and the normal behavior will take place.
\ddg{Explain the weights of the edges introduced by the unknown nodes}

\section{Modeling as a Constraint Optimization Problem \label{SEC:CP}}
\subsection{Definitions}
A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
(w.l.o.g.) minimized. 
A valuation such that all variables in $\boldsymbol{v}$ map 
to exactly one value, and all the constraints in $C$ are satisfied by the 
valuation is a \emph{solution} to $P$. A solution $\theta$ is optimal if$\not 
\exists \theta', \theta'(\boldsymbol{v}) < \theta(\boldsymbol{v})$.

@@

%\subsection{Constraint Programming}
Constraint Programming (CP) allows the user to model a COP and give it 
to a solver that will find solutions to the COP and while optimizing 
the objective function (and prove optimality).

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ in turn. At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change it's 
last decision. \ignore{The choice of the order of the variables to be assigned, 
and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}}.

Since only using a backtracking algorithm would have a prohibitive cost, CP 
uses a combination of search and \emph{propagation}. The latter is achieved by 
\emph{propagating} the last decision made via specialized algorithms called 
\emph{propagators}. A propagator is a function that removes inconsistent values 
form the domains of variables. That way, values that cannot appear in a 
solution givent eh current set of decisions are never tried by the search.

\emph{Global constraints} are higher order constraints that enforce a 
complex 
constraint over a set of variables. These are typically implemented with 
propagators that use specific algorithms for these 
constraints and perform substantially better than a decomposition approach
\cite{regin1994filtering,beldiceanu2012global}.

@@

\begin{flalign}
	& \text{Minimize~~} w_{STP} + w_{ADIFF} - w_{PAT}
	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
	%w_\mathcal{I}(e) + \sum_{e \in \mathcal{M}_\mathcal{O}^{s^\star}} c_e * 
    %		w_\mathcal{I}(e)
	\label{EQ:obj}&&\\
	&\text{such that~~}  \nonumber&& \\
	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
	&&\\
	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\
	&\forall d \in \mathcal{D_{G_O}}, c_d \Leftrightarrow degree(d) = 1 
	\label{EQ:deg2}&&\\
	&\forall a \in \mathcal{A}_{s^\star}, match[a] \in \{ d | (a,d)\in 
	\mathcal{M}_\mathcal{O}^{s^\star} \} \label{EQ:matchdom}&&\\
	& \textit{alldifferent}(match) \label{EQ:alld}&& \\
	& \forall a \in \mathcal{A}_{s^\star}, c_{match[a]} = \mathit{true} 
	\label{EQ:map}&&\\
	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
	\label{EQ:matchcost}  &&\\
	& \forall p \in \mathcal{P}, \big(\forall e\in edges(p), c_e = 
	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
	\label{EQ:pcost} &&\\
	& c_{unknown} \Rightarrow \big( c_{root}  \land 
	c_{(unknown,root)} \big) \label{EQ:unk}
\end{flalign}

Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
enforces that the solution 
$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
of the alignment graph 
and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. \ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. Eq. 
\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph.} Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute, which has to be one of 
the ones for which an edge existed. Eq. \ref{EQ:map} ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. Eq. 
\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by using patterns.
Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
is connected to \emph{root}.
Notice how there is no further requirement for unmatched attributes, as the 
$unk_i$ data nodes behave like normal data nodes, and the connectedness 
requirement will make sure that \emph{root} is connected to the rest of the 
tree (i.e. the semantic model).

@@

% baseline for evaluation
We choose \emph{Karma}~\cite{taheriyan2016learning} as our baseline.
This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
However, they use heuristic algorithms both for the matching and for the STP parts.
They solve the problems sequentially, i.e., once they produce a set of candidate mappings for attributes into the ontology, they fix this set and move onto the STP part.
Additionally, they do not consider unmatched attributes in the sources.
To ensure that Karma also handles such attributes, we change its semantic labeling model SemanticTyper~\cite{Ramnandan:Assigning} to ours and we add a special \emph{unknown} ontology which gives specification for \emph{root} and \emph{unknown} nodes of the alignment graph.
The first modification also ensures the fairness of evaluation since both Karma and Serene will have the same matches for attributes.

@@

% architecture
We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics, AWS machine is bigger}
In all our experiments we use a timeout threshold of 15s for the chuffed solver.

@@

To evaluate our new system \emph{serene}, we show that its semantic labeling model produces more accurate matches for attributes and the CP formulation leads to better semantic models in terms of precision and recall.

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
Our intution why our approach performs better is that we have encorporated features which are derived directly from attribute values and are not based on the notion of similarity.
\npr{Good enough explanation?}

\begin{table}[t]\small
  \centering
  \caption{Average performance of semantic labeling models for leave one out strategy.}
  	\label{tab:semlab}
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & \multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

>>>>

\usepackage{tikz}
\tikzset{every picture/.style={font issue=\small},
         font issue/.style={execute at begin picture={#1\selectfont}}
        }
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{arrows,shapes,decorations.pathmorphing}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{mindmap,backgrounds}
\tikzstyle{class}=[draw,green,ellipse,align=center,fill=green!25,text=black]
\tikzstyle{data}=[draw,rectangle,align=center,black!70]
\tikzstyle{att}=[rectangle,align=center,fill=brown!70!red]
\tikzstyle{hasaA} = 
[draw,densely dashed,-,black!70,decoration={snake,segment 
length=10,amplitude=0.3,post length=4}]
\tikzstyle{hasaC} = [>=stealth',draw,thick,-, black]
\tikzstyle{isa} = [>=o,draw,densely dotted,very thick,black!90]

@@

\newcommand{\minizinc}{\textsc{MiniZinc}}
\newcommand{\chuffed}{\textsc{Chuffed}}
\newcommand{\relonto}{\textsc{Rel2Onto}}
\newcommand{\karma}{\textsc{Karma}}
\newcommand{\serene}{\textsc{Serene}}
\newcommand{\serenepats}{\textsc{SerenePats}}

@@

Firstly, we build an \emph{integration graph} which includes the 
attributes from the new source as well as ontology classes and properties. 
Secondly, we apply machine learning techniques to 
assign costs to its edges. 
Lastly, we use Constraint Programming (CP) to 
find a minimum cost Steiner Tree in the graph.
The goal is to assign the costs on the edges in such a way that the resulting 
Steiner Tree is a valid and coherent semantic model for the new source. 
We call our system \serene{}.

@@

Section \ref{SEC:problem} formally states the problem. 
In Section \ref{SEC:ML} we present how we convert the information given into a 
useful data representation. 
Section \ref{SEC:STP} shows how we model the problem as a STP, 
whereas Section \ref{SEC:CP} discusses how we implement the model in CP. 
Section \ref{SEC:Res} shows our results. 
Section \ref{SEC:pw} presents the previous work done to achieve this task.

@@

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
$ \mathcal{C}_m$ corresponds to classes in the ontology 
whereas $\mathcal{D}_m$ corresponds to data 
properties. 
Edges in the semantic model correspond to properties in the ontology, as 
shown in Fig.~\ref{FIG:onto} and \ref{FIG:sem}.
The semantic model may have several instances of a same ontology class or 
object property.

@@

We formulate the problem of semantic labeling as a multi-class classification
problem.
The known source descriptions $S_T$ provide us the training sample.
We compute a feature vector for each attribute in a data source and associate 
the known semantic type with the corresponding feature vector.
The feature vector includes characteristics of the attribute such as a number 
of whitespaces and other special characters, statistics of values in the column 
(e.g, mean/max/min string length and numeric statistics) and more. A full 
list can be found in appendix \ddg{Apendix!}
One of the important features characterising information content of an attribute is Shannon's entropy of the attribute's concatenated rows.
Shannon's entropy (or information entropy~\cite{Manning:Introduction}) of a string $X$ is defined as
$H(X) = -\sum_{i}{p_i \log_{2}p_i},$ where $p_i$ is the probability of a character, whose index in character vocabulary is $i$, to appear in $X$, and the summation ranges over all
characters in the vocabulary of all possible characters.
To evaluate $p_i$ in Shannon's entropy, we evaluate normalized character frequency distribution \emph{chardist} of an attribute, as character counts in concatenated rows of the attribute, normalized by the total length of the concatenated rows.
The vocabulary of all characters consists of 100 printable characters (including $\backslash$n).
Finally, we add the 100-dimensional vector of $p_i$ to the attribute feature vector.
We also compute a set of features based on similarity metrics inspired by state-of-the-art works~\cite{Pham:semantic} or~\cite{Ritze:matching}.
Among others, we compute mean cosine similarity for character distributions of attribute values and string similarity metrics for attribute names.
%To extract features from attribute names, we compute string similarity metrics: minimum edit distance, two WordNet based similarity measures such as JCN~\cite{Jiang:Semantic} and LIN ~\cite{Lin:Information}, and $k$-nearest neighbors using Needle-Wunsch distance~\cite{Needleman:General}.
%The minimum edit distance between two strings $s_1$ and $s_2$ is the minimum number of edit operations, such as insertion, deletion, substitution, which are required to transform one string into another~\cite{Manning:Introduction}.
%We compute the similarity between attribute name and all class instances in the training data.
%The number of thus extracted features depends on the number of semantic labels in the training data.
We train a random forest on the obtained sample.

@@

Note that we keep all the matches, regardless of the confidence fo the match. 
This is an important difference between our system and other approaches 
\cite{taheriyan2016learning} that 
remove some of the matches based on heuristics to then simplify the task of 
finding the semantic model.

@@

The algorithm we use for the construction of the alignment graph 
$\mathcal{G_O}$ was given by~\cite{taheriyan2016learning}.
Briefly, the algorithm has three parts:
%\begin{enumerate}
$(i)$ %\item 
Adding the known semantic models
$(ii)$ %\item 
Adding the semantic types learned for the target source
%\item 
$(iii)$ Expanding the graph using the domain ontology $\mathcal{O}$.
%\end{enumerate}

Note how the alignment graph contains data nodes that correspond to semantic 
types. 
For instance, it could contain two nodes $City.name$ and $State.name$ rather than just one node $name$ connected to two 
nodes $City$ and $State$. 
We say these nodes are \emph{induced} into the 
alignment graph by the semantic types.
We denote them as $\mathcal{D_{G_O}}$ and call them the \emph{data nodes} of the alignment graph.

The graph is weighted by a function $w_\mathcal{O} : \mathcal{E_O} \mapsto 
\mathbb{R}$ in 
such a way that edges which are present in
the known semantic models have lower weights than those 
which are inferred from the ontology.
As we will see in the next section, this makes edges present in semantic models 
more attractive. 
Details on the weighting function can be found in \cite{taheriyan2016learning}.
%\ddg{How exactly are they weighted?}

An example alignment graph is illustrated in Fig.~\ref{FIG:ali}. 
%Bigger examples can be found in \cite{Taheriyan2013}. 
Black links correspond to the links which are supported by the known semantic models. 
Blue and orange links are inferred from the ontology $\mathcal{O}$ (the orange 
ones correspond to the ones added to connect Classes of the ontology that never 
appeared in the semantic models).
% and can be assigned the 
%maximum weight $w_max$ \ddg{where does this weight come from?}

@@

	\node[class,orange,fill=orange!30!white,text=black] (PL) at (3,\ysh/2)  
	{\small 
	Place};

@@

\end{tikzpicture}
\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black] () at 
(0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\end{figure}

@@

We associate a weighting function  $w_\mathcal{I} : E \mapsto \mathbb{R}^+$ to 
the integration graph. For an edge $e \in \mathcal{E_O}$, $w_\mathcal{I}(e) = 
w_\mathcal{O}(e)$. For an edge $e 
\in \mathcal{M}_\mathcal{O}^{s^\star}$ connecting attribute $a_i$ to the node 
$l_j$ induced by the semantic model, $w_\mathcal{I}(e) = - 
ln(\psi(a_i,l_i))$. %\ddg{CHECK!}

@@

\subsection{Unmatched Attributes}
It is common that the data sources to be integrated will have columns that 
simply can't be matched to the ontology.
This can happen when a column of a source table contains some information that 
is uninteresting to the user, or because the ontology has not been properly 
designed. 
Examples of these situations can be found in domain specific data 
\cite{Pham:semantic} or HTML tables \cite{Ritze:matching}.
In current systems, these columns are removed in a process that requires 
extra time and effort as this is typically done manually in the real world.

@@

If an attribute $a$ is matched to $unk_a$, then $unk_a$ will be linked to Class 
node \emph{unknown}. 
The rest of the attributes can then be matched normally 
and build  a semantic model as usual. 
Then, to maintain connectedness of the 
Steiner tree, the \emph{unknown} node and one of the other selected Class nodes 
will 
both be connected to the \emph{root} node. 
Note that if all attributes find a 
match, then both the \emph{unknown} and \emph{root} won't be selected in the 
Steiner tree and the normal behavior will take place.
\ddg{Explain the weights of the edges introduced by the unknown nodes}

\section{Modeling in Constraint Programming \label{SEC:CP}}
\subsection{Definitions}
A Constraint Optimization Problem (COP) is a tuple $P = (\boldsymbol{v},C,o)$ 
where $\boldsymbol{v}$ is a 
set of \emph{variables}, $C$ is a set of $n$-ary 
\emph{constraints} over variables $\boldsymbol{v}$ and $o$ is an 
\emph{objective function} $o : \boldsymbol{v} \mapsto \mathbb{R}$ to be 
(w.l.o.g.) minimized. 
A valuation such that all variables in $\boldsymbol{v}$ map 
to exactly one value, and all the constraints in $C$ are satisfied by the 
valuation is a \emph{solution} to $P$. A solution $\theta$ is optimal if$\not 
\exists \theta', \theta'(\boldsymbol{v}) < \theta(\boldsymbol{v})$.

@@

%\subsection{Constraint Programming}
Constraint Programming (CP) allows the user to model a COP and give it 
to a solver that will find solutions while optimizing 
the objective function (and prove optimality).

Briefly, the way a CP solver works is by assigning a value to each variable of 
$\boldsymbol{v}$ in turn. At each iteration it will check whether any 
constraint in $C$ is violated, in which case it will backtrack to change it's 
last decision. \ignore{The choice of the order of the variables to be assigned, 
and the 
choice of the value to be assigned to each variable is called the \emph{search 
strategy}}.
Since only using a backtracking algorithm would have a prohibitive cost, CP 
uses a combination of search and \emph{propagation}. The latter is achieved by  
removing inconsistent values 
form the domains of variables. That way, values that cannot appear in a 
solution, given the current set of decisions, are never tried by the search. 
\emph{Global constraints} are higher order constraints that enforce a 
complex 
constraint over a set of variables. These are typically implemented with 
specialized algorithms for these 
constraints and perform substantially better than a decomposition approaches
\cite{regin1994filtering,beldiceanu2012global}.

@@

\begin{flalign}
	& \text{Minimize~~} w_{STP} + w_{ADIFF} - w_{PAT}
	%\sum_{e \in \mathcal{E}_\mathcal{O}}c_e * 
	%w_\mathcal{I}(e) + \sum_{e \in \mathcal{M}_\mathcal{O}^{s^\star}} c_e * 
    %		w_\mathcal{I}(e)
	\label{EQ:obj}~~~\text{such that~~} && \\
	& \textit{steiner}(\{c_n| n \in \mathcal{V_O}\},\{c_e| e \in 
	\mathcal{E_O}\},\mathcal{G_O},w_\mathcal{O},w_\mathit{STP})  \label{EQ:stp} 
	&&\\
	&\forall d \in \mathcal{D_{G_O}}, degree(d) \leq 1 \label{EQ:deg1}&&\\
	&\forall d \in \mathcal{D_{G_O}}, c_d \Leftrightarrow degree(d) = 1 
	\label{EQ:deg2}&&\\
	&\forall a \in \mathcal{A}_{s^\star}, match[a] \in \{ d | (a,d)\in 
	\mathcal{M}_\mathcal{O}^{s^\star} \} \label{EQ:matchdom}&&\\
	& \textit{alldifferent}(match) \label{EQ:alld}&& \\
	& \forall a \in \mathcal{A}_{s^\star}, c_{match[a]} = \mathit{true} 
	\label{EQ:map}&&\\
	& w_{\mathit{ADIFF}} = \sum_{(a,d) \in \mathcal{M}_\mathcal{O}^{s^\star}} 
	w_\mathcal{I}(~(a,d)~) * \llbracket match[a] = d\rrbracket 
	\label{EQ:matchcost}  &&\\
	& \forall p \in \mathcal{P}, \big(\forall e\in edges(p), c_e = 
	\mathit{true} \big) \Leftrightarrow c_p \label{EQ:patt}&&\\
	& w_{PAT} = \sum_{p\in\mathcal{P}} w_\mathcal{P}(p)* c_p 
	\label{EQ:pcost} &&\\
	& c_{unknown} \Rightarrow \big( c_{root}  \land 
	c_{(unknown,root)} \big) \label{EQ:unk}
\end{flalign}

Eq. \ref{EQ:obj} is the objective function: we are minimizing the cost 
of $T^\star$ while collecting prizes for each pattern we use. Eq. \ref{EQ:stp} 
enforces that the solution 
$T^\star$ is indeed a tree defined by the $c_n$ and $c_e$ variables, subgraph 
of the alignment graph 
and of total weight $w_{STP}$. Equations \ref{EQ:deg1} and \ref{EQ:deg2} ensure 
that if a data node of the alignment graph is selected, then at most one edge 
reaches it (from the side of the alignment graph) and otherwise it is 
disconnected. \ignore{Eq. \ref{EQ:matchdom} ensures that the domain of each 
variable in 
the array $match$ corresponds to a subset of data nodes of the alignment graph 
for which there is an edge connecting to the attribute at hand. Eq. 
\ref{EQ:alld} ensure that each attribute is mapped to exactly one data node of 
the alignment graph.} Equations \ref{EQ:matchdom} and \ref{EQ:alld} ensure that 
there is exactly one data node matched to an attribute. Eq. \ref{EQ:map} 
ensures that 
if a data node of the alignment graph has been mapped to some attribute, then 
that data node must be in the solution tree, and vice-versa. Eq. 
\ref{EQ:matchcost} computes the cost $w_{ADIFF}$ of the matches.
Eq. \ref{EQ:patt} indicated that a pattern is used if and only if all its edges 
are selected in the tree. Eq. \ref{EQ:pcost} computes the prizes collected by using patterns.
Eq. \ref{EQ:unk} ensures that if the \emph{unknown} class node is used, then it 
is connected to \emph{root}.
Notice how there is no further requirement for unmatched attributes, as the 
$unk_i$ data nodes behave like normal data nodes, and the connectedness 
requirement will make sure that \emph{root} is connected to the rest of the 
tree (i.e. the semantic model).

@@

% baseline for evaluation
We choose \karma{}~\cite{taheriyan2016learning} as our baseline.
This system also phrases the \relonto{} problem as STP and decomposes it further into two parts.
However, they use heuristic algorithms both for the matching and for the STP parts.
They solve the problems sequentially, i.e., once they produce a set of candidate mappings for attributes into the ontology, they fix this set and move onto the STP part.
Additionally, they do not consider unmatched attributes in the sources.
To ensure that \karma{} also handles such attributes, we change its semantic 
labeling model, SemanticTyper~\cite{Ramnandan:Assigning}, to ours and we add a 
special \emph{unknown} ontology which gives specification for \emph{root} and 
\emph{unknown} nodes of the alignment graph.
The first modification also ensures the fairness of evaluation since both 
\karma{} and \serene{} will have the same matches for attributes.

@@

% architecture
We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics, AWS machine is bigger}
In all our experiments we use a timeout threshold of 15s for \chuffed{}.

@@

To evaluate our new system \serene{}, we show that its semantic labeling model 
produces more accurate matches for attributes and that the CP formulation leads 
to better semantic models in terms of precision and recall.

\ignore{We have developed a new approach for semantic labeling which can 
efficiently handle the \emph{unknown} class.}
\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
approach DSL~\cite{Pham:semantic}. } %Repeat from above
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class.
It is clear that we cannot directly speak about similarity for unmatched attributes, since they are rather dissimilar from known semantic types.
Our intution why our approach performs better is that we have encorporated features which are derived directly from attribute values and are not based on the notion of similarity.
\npr{Good enough explanation?}

\begin{table}[!ht]\small
  \centering
  \caption{Average performance of semantic labeling models for leave one out strategy.}
  	\label{tab:semlab}
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & 
  		\multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.56 & 0.618 & 156.6 & 36.3\\
 		Serene & 0.866 & 0.827 & 100.6 & 6.8\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

\begin{figure}[!htb]
\begin{minipage}[b]{.5\linewidth}
\centering
\hspace*{-15pt}
\begin{tikzpicture}[baseline,scale=0.47]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    style = {font=\huge}
		]
